\textbf{Pillar 2: Topological Resilience and Geometric Memory}

3D disorder (β ≈ 0.91) triggers spontaneous self-healing via the "Golden
Attractor," realigning with 6D templates. This redefines material
"impossibility": Catastrophic melting requires no external energy for
recovery, as the 6D lattice exerts topological force.

Evidence: Simulations in generate\_figure2\_entropy.py show β jumps from
chaotic 0.9097 to golden resonance 1.734, minimizing phason strain
E\_\{phason\} = \textbackslash sum
\textbar\textbar x\_i\^{}\textbackslash perp\textbar\textbar\^{}2 in r=7
windows; counts 313 discrete phason flips during snap-back
(ENTROPY\_EFFICIENCY\_VALIDATION.csv). Entropy decay is 246x faster than
cubic grids, confirming 20.5\% efficiency gain.

\textbf{Pillar 3: Scaling Laws, Depletion Constant, and Entropy Delay}
chaos-to-recovery (313 phason flips), validating Pillar 2.

II. Advanced Simulation Scripts (simulations/)

navier\_stokes\_lattice\_cap.py: Demonstrates bounded vorticity on n=12
lattices vs. standard grids, verifying Pillar 1.

icosahedral\_airfoil\_sim.py: Implements low-drag wing (Cd ≈
0.002--0.005, 80\% reduction), tying to Pillar 1.

phason\_slip\_detector.py: Analyzes phason slips (deviations ≈ 0.86),
supporting Pillar 3.
from dat\_universal\_engine.py (Pillar 2).

appendix\_g\_thermal.tex: Thermal parameters (T\_source = 1000°C,
Anderson localization), with bandgap plots (Pillar 4).

IV. Manuscript Source and Reproducibility Tools (manuscript/)

dat\_manuscript.tex: Full LaTeX source with integrated pillars, figures
(e.g.,
\textbackslash includegraphics\{DAT\_3.0\_Phase\_Comparison.pdf\}), and
citations.

dat\_manuscript.pdf: Compiled draft.

validate\_results.py: Recomputes metrics (β jumps, δ₀) from CSVs for
verification.

run\_all\_sims.sh: Bash script executing sweeps and generating
figures/logs.

dockerfile: Containerizes environment for reproducibility.

V. Interactive Notebooks (notebooks/)

e6\_resilience.ipynb: Replicates E6 simulations (β from 0.91 to 1.73),
with inline plots (Pillar 2).

density\_hypothesis.ipynb: Compares β peaks across lattices, validating
scaling with kissing numbers (Pillar 3).
